\chapter{Citations \& Users of Mininet WiFi}

\section{Research papers using Mininet-WiFi}

\begin{itemize}
\item \textit{Seongjin Park and Younghwan Yoo}. \textbf{Network Intelligence based on Network State Information for Connected Vehicles Utilizing Fog Computing
}. Journal - Mobile Information Systems.
\\
\item \textit{Felipe S. Dantas Silva, Augusto Neto, Douglas Maciel, José Castillo-Lema, Flávio Silva, Pedro Frosi and Eduardo Cerqueira}. \textbf{An Innovative Software-Defined WiNeMO Architecture for Advanced QoS-Guaranteed Mobile Service Transport}. Journal - Computer Networks, 2016. ISSN: 1389-1286, DOI: http://dx.doi.org/10.1016/j.comnet.2016.04.019.
\\
\item Talles Quintao Pessoa, Guilherme Melo de Oliveira Rodrigues, Lucas Soares da Silva and Fatima Duarte-Figueiredo. \textbf{Avaliação, Através de Simulação e Teste Real, de um Firewall Baseado em SDN}. Available at: http://www.academia.edu/download/46340080/Avaliacao\_de\_\\Firewall.pdf
\\
\item Nikolaos E. Petroulakis, George Spanoudakis and Ioannis G. Askoxylakis. \textbf{Patterns for the design of secure and dependable software defined networks}. Available at: http://dx.doi.org/10\\.1016/j.comnet.2016.06.028.
\\
\item \textbf{SDN sobre redes IEEE 802.11: simulación mediante MiniNet-Wifi}. Available at:\\ https://repositorio.unican.es/xmlui/handle/10902/9330
\\
\item Wang, Zeng and Zhou, Jinhe. \textbf{Power Control Mechanism in Software Defined Wireless Networking}. IEEE Communication Software and Networks (ICCSN), pages 428--431, 2016.\\

\item  Daikai Tu, Zhifeng Zhao and Honggang Zhang. \textbf{ISD-WiFi: An intelligent SDN based solution for enterprise WLANs}.  Wireless Communications \& Signal Processing (WCSP) doi: 10.1109/WCSP.2016.7752738, Oct, 2016.\\

\item Jafar Badarneh, Yaser Jararweh, Mahmoud Al-Ayyoub, Mohammad Al-Smadi and
Ramon Fontes. \textbf{Software Defined Storage for Cooperative Mobile Edge Computing System}. International Conference on Software Defined Systems (SDS 2017), Valencia, Spain, 2017.\\

\item Christos Bouras, Anastasia Kollia and Andreas Papazois. \textbf{Teaching 5G Networks Using the ONOS SDN Controller}. ICUFN, Milan, Italy. 2017.

\end{itemize}


\section{Users}
\textbf{Who uses our tool? Please, let us know}
\\

\begin{itemize}
\item Dr. Chih-Heng Ke Department of Computer Science and Information Engineering, National Quemoy University, Kinmen, Taiwan. \url{http://csie.nqu.edu.tw/smallko/sdn/sdn.htm}
\item Brian Linkletter: \url{http://www.brianlinkletter.com/mininet-wifi-software-defined-network-emulator-supports-wifi-networks/}
\item Code Project: \url{http://www.codeproject.com/Tips/1064353/Using-Mininet-wifi-to-Simulate-Software-Defined-Wi}
\item Selection of Offloading Algorithms in Highly Congested SDNs: \url{https://dspace.library.colostate.edu/bitstream/handle/11124/170940/SDNPoster_Grads.pdf?sequence=1&isAllowed=y}
\item Analisi dell’emulatore per Software-defined wireless networks Mininet-WiFi: \url{http://www.ingegneria-informatica.unina.it/sites/default/files/elaborati_tesi/2017/05/Elaborato\%20Esposito\%20Oreste\%20N46000284.pdf}
\end{itemize}


\section{Citing Mininet-WiFi}
\textbf{Please use:}
\\
R. R. Fontes, S. Afzal, S. H. B. Brito, M. A. S. Santos and C. E. Rothenberg, "Mininet-WiFi: Emulating software-defined wireless networks," Network and Service Management (CNSM), 2015 11th International Conference on, Barcelona, 2015, pp. 384-389. doi: 10.1109/CNSM.2015.7367387 URL: http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=\&arnumber=7367387\&isnumber=7367318
.bib(http://\\www.bibsonomy.org/bib/bibtex/2b4f6ac6538a6228f2eb78e24db7cdc2c/chesteve)

@INPROCEEDINGS{7367387, author={R. R. Fontes and S. Afzal and S. H. B. Brito and M. A. S. Santos and C. E. Rothenberg}, booktitle={Network and Service Management (CNSM), 2015 11th International Conference on}, title={Mininet-WiFi: Emulating software-defined wireless networks}, year={2015}, pages={384-389}, keywords={software defined networking;virtualisation;wireless LAN;IEEE 802.11;Mininet-WiFi;network virtualization;software defined network;software-defined wireless network emulation;wireless OpenFlow-SDN scenarios;Emulation;IEEE 802.11 Standard;\\Linux;Protocols;Topology;Wireless networks;Emulation;OpenFlow;SDN;Wireless networks}, doi={10\\.1109/CNSM.2015.7367387}, month={Nov},}