\chapter{Publications}

\section{SDN For Wireless 2015}
\textit{Exhibit}\\
Fontes, R. R., Afzal, S., Brito, S. H. B., Santos, M., Rothenberg, C. E. “Towards an Emulator for Software Defined Wireless Networks“. In EAI International Conference on Software Defined Wireless Networks and Cognitive Technologies for IoT. Rome, Italy, Oct 2015.

\section{CNSM 2015 - Best Paper Award!}
\textit{This paper explains the basic Mininet-WiFi design and useful Case Studies.}
\\
Fontes, R. R., Afzal, S., Brito, S. H. B., Santos, M., Rothenberg, C. E. “Mininet-WiFi: Emulating Software-Defined Wireless Networks“. In 2nd International Workshop on Management of SDN and NFV Systems 2015. Barcelona, Spain, Nov 2015.

\section{SwitchOn 2015}
\textit{This paper presents a demo use case in a mobile video streaming scenario to showcase the ability of Mininet-WiFi to emulate the wireless channel in terms of bandwidth, packet loss, and delay variations as a function of the distance between the communicating parties.}\\
Fontes, R. R., Rothenberg, C. E. Towards an Emulator for Software-Defined Wireless Networks. In: SwitchOn 2015, São Paulo – SP – Brazil.

\section{SBRC 2016}
\textit{DEMO}\\
Ramon dos Reis Fontes and Christian Esteve Rothenberg. Mininet-WiFi: Emulação de Redes Sem Fio Definidas por Software com suporte a Mobilidade. In Simpósio Brasileiro de Redes de Computadores e Sistemas Distribuídos (SBRC 2016) - Salão de Ferramentas, 2016, Salvador - BA - Brazil.

\section{SIGCOMM 2016}
\textit{DEMO}\\
Ramon dos Reis Fontes and Christian Esteve Rothenberg. Mininet-WiFi: A Platform for Hybrid Physical-Virtual Software-Defined Wireless Networking Research (SIGCOMM 2016) - 2016, Florianopolis - ES - Brazil.

\section{Institute of Electrical and Electronics Engineers - IEEE 2017}
\textit{In this paper, we enumerate the potentials of software-defined vehicular networks, analyse the need of rethinking the traditional SDN approach from theoretical and practical standpoints when applied in this application context, and present an emulation approach based on the proposed node car architecture in Mininet- WiFi to showcase the applicability and some expected benefits of SDN in a selected use case scenario.}\\
Ramon dos Reis Fontes and Claudia Campolo and Christian E. Rothenberg and Antonella Molinaro. From Theory to Experimental Evaluation: Resource Management in Software-Defined Vehicular Networks (IEEE Access 2017), DOI: 10.1109/access.2017.2671030.

\section{The Computer Journal 2017}
Ramon dos Reis Fontes and Mohamed Mahfoudi and Walid Dabbous and Thierry Turletti and Christian Rothenberg. How Far Can We Go? Towards Realistic Software-Defined Wireless Networking Experiments, Oxford University Press ({OUP}), DOI: 10.1093/comjnl/bxx023.